%!TEX TS-program = xelatex
\documentclass[]{perezpaya-cv}

\begin{document}
\header{alejandro}{perezpaya}
       {Software Developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
  	04-27-1996
    Victoria Rubio nº1, 14
    28660 Boadilla del Monte
    Spain
    ~
    \href{mailto:alejandro@perezpaya.net}{alejandro@perezpaya.net}
    \href{http://perezpaya.net}{http://perezpaya.net}
    \href{http://github.com/alexperezpaya}{Github}
  \section{languages}
    Spanish - Native
    English - Fluent
    Chinese - Beginner
    French  - Beginner
  \section{programming}
	Swift
    Objective-C
    Ruby
    Javascript
    (Node.js \& Browser)
    Golang
    Python
    PHP
    HMTL5 \& CSS3
\end{aside}

\section{interests}
programming, music, physics, soccer, basketball, economy, business, politics, philosophy

\section{education}

\begin{entrylist}
  \entry
    {2008-2011}
    {Chinese Simplified}
    {Eurocolegio Casvi Boadilla}
    {\emph{Extracurricular lessons.}}
  \entry
    {2008-2012}
    {High School: ESO}
    {Eurocolegio Casvi Boadilla}
    {Specialisation in Science\\
    Biology, Computer Science, Physics, Technical Drawing, Science Maths and Economics as subjects}
  \entry
    {2012–2014}
    {Science Baccalaureate}
    {Eurocolegio Casvi Boadilla}
    {Physics, Technical Drawing, Science Maths and Economics as subjects}
  \entry
    {2014}
    {Computer Science Degree}
    {Technical University of Madrid}
    {}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {09-12 10-13}
    {Inevio, formerly known as weeZeel}
    {Backend Developer}
    {Worked here as Backend Developer with Node.js, wrote the core of the actual project}
  \entry
    {06-14 11-14}
    {Fever}
    {iOS Developer}
    {Fever \emph{Plans marketplace app with custom suggestion based on your interests} \\VIPER based app, 1 million downloads in the store. Top 1 a few times in Spanish App Store. Test suite done with Kiwi and automated releases based on Shenzen}
  \entry
    {11-14-11-15}
    {Cabify}
    {iOS Developer}
    {\emph{On demand cars with driver plus reservation service.}
    \\Maintained old app, and created from scratch the brand new app due to the failures in the core made before I joined. Socket powered state machine application architecture in journey management and VIPER architecture for the CRUD side, accounts, reservations, etc.. Test Driven development made}
  \entry
    {since 11-15}
    {ermes}
    {iOS Developer}
    {At ermes we are working hard to build a product that solves the problems regarding last mile in package deliveries}
\end{entrylist}

\section{code}
\begin{entrylist}
\entry
    {Swift}
    {Jukebox}
    {\href{http://github.com/alexperezpaya/Jukebox}{github.com/alexperezpaya/Jukebox}}
    {Wrote a simple iTunes Library Management as an iOS example project
Swift \& Objective-C projects. Same functionality. This is the Swift version. I felt really comfortable writing this app in Swift.}

\entry
    {Swift}
    {Jukebox-Objc}
    {\href{http://github.com/alexperezpaya/Jukebox-Objc}{github.com/alexperezpaya/Jukebox-Objc}}
    {This is the Objective-C version of the Jukebox app. Wrote it just before finishing the Swift one, after using Swift I felt I was going slower here, even I just had to translate what I did in Swift, those commodities earned in Swift made this one a bit harder. Even thought, it was a great experience doing it.}

\end{entrylist}

\section{applications\&projects}

\begin{entrylist}
  \entry
    {2014}
    {Fever}
    {\href{http://feverup.com}{feverup.com}}
    {Developed and maintained this application, Facebook, REST API, AFNetworking, Dependency Injection, VIPER, Core Data, Memory Storage}
  \entry
    {2014-now}
    {Cabify}
    {\href{http://cabify.com}{cabify.com}}
    {Uber competitor for Latam and Spain (business focused), VIPER architecture, WebSockets, AFNetworking, StateMachine Architecture to handle multiple journey states received in socket }
  \entry
    {2014}
    {Vonsai}
    {\href{https://github.com/vonsai/ios}{github.com/vonsai/ios}}
    {Swift app made in 24h. We simply defined it like a Tinder for News. Like or dislike summarised news and with those few taps you build your daily newsfeed. We won UX prize at elmundo.es (Newspaper) hackathon.}
  \entry
    {2015}
    {Pentagon}
    {\href{https://github.com/pentagonerino/iOS}{github.com/pentagonerino/iOS}}
    {Swift iOS app made in 2 days for SnapPayments hackathon. We built an application that allowed people to buy items in a museum with their NFC-Card (Serialport connected device) or scanning their card with Card.io. Won 3rd prize.}
  \entry
    {2015}
    {Krytpe}
    {\href{https://github.com/krypteauth/ios}{github.com/krypteauth/ios}}
    {Swift iOS app doing frontend for your own server that runs a decentralized authorizations backend. Developed in a 18h security hackathon.}
  \entry
    {2015}
    {Parkfy}
    {\href{https://parkfy.com}{parkfy.com}}
    {Swift Freelance MVP Application made using MVVM Architecture. Alamofire, Argo and XLForm used in the app as external libraries.}
  \entry
    {2015-now}
    {Taylor}
    {\href{http://github.com/izqui/Taylor}{github.com/izqui/taylor}}
    {Contributor and developer of this project made for fun with my pal @izqui. CocoaAsyncSocket based and Swift oriented.}
\end{entrylist}

\end{document}
